Realizing temporal graphs from fastest travel times

### 2024-01-19 Figures/fig-fpt-equivClass.tex
small change to fig

		\draw (z1) edge[] node[below, yshift=-1mm, text=black] {$t_1$}  (x);
		\draw (z2) edge[] node[above, yshift= 1mm,  text=black] {$t_2$} (x);
		\draw [red]
		(x) edge[] [bend right] node[below, text=black] {$P$} 
		node[vert, pos=0.87, color=black, fill=white] {}
		node[pos=0.96,below, text=black] {$t_p$} (y) ;
		\draw [blue]
		(x) edge[] [bend left] node[above, text=black] {$Q$} 
		node[vert, pos=0.87, color=black, fill=white] {}
		node[pos=0.96,above, text=black] {$t_q$}
		(y) ;

>>>>

		\draw (z1) edge[] node[below, pos=0.6, yshift=-1mm, text=black] {$t_1$}  (x);
		\draw (z2) edge[] node[above, pos=0.6, yshift= 1mm,  text=black] {$t_2$} (x);
		\draw [red]
		(x) edge[] [bend right] node[below] {$P$} 
		node[vert, pos=0.87, color=black, fill=white] {}
		node[pos=0.96,below, text=black] {$t_p$} (y) ;
		\draw [blue]
		(x) edge[] [bend left] node[above] {$Q$} 
		node[vert, pos=0.87, color=black, fill=white] {}
		node[pos=0.96,above, text=black] {$t_q$}
		(y) ;
